---
title: "Notes on the package utilities"
author: "Stéphane Laurent"
date: "27 février 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, eval=FALSE}
devtools::install_version("SLutils", version="1.4.11", dependencies=FALSE, build_vignettes=FALSE, repos=c(SL = "file:///Y:/7. STAT ANALYSES and IA/71- IA/LocalApps/CRANlike-SL"), type="source")
```

- Latest version (see below)

```{r, eval=FALSE}
devtools::install_version("SLutils", version="1.4.12", dependencies=FALSE, build_vignettes=FALSE, repos=c(SL = "file:Y:///7. STAT ANALYSES and IA/71- IA/LocalApps/CRANlike-SL"), type="source")
Warning: package incorrect 'Y:/7.'
Warning: package incorrect 'STAT'
Warning: package incorrect 'ANALYSES'
Warning: package incorrect 'and'
Warning: package incorrect 'IA/71-'
Warning: package incorrect 'IA/LocalApps/CRANlike-SL/src/contrib/SLutils_1.4.12.tar.gz'
Erreur : ERREUR : aucun package spécifié
```

____

-	For type=”source”: `devtools::install_version` runs its specific machinery when the version is an old one.

-	For type=”source” and the latest version, it runs the classical install.packages; the issue with the white spaces comes from install.packages.

-	For type=”binary”, I have to modify my code and this will be ok for any version.

___

my issue (see also my modifs in packrat): <https://github.com/hadley/devtools/issues/1426> 

## Solve the white-spaces issue 

`shortPathName` ? yes (see below)

Only problem: the slashes... (?)

## Path given by network drive name

```{r}
p <- "//Rixdsntp001/cmcstat/7. STAT ANALYSES and IA/71- IA/LocalApps/CRANlike-SL"
shortPathName(p)
"\\\\Rixdsntp001\\cmcstat\\7~1.STA\\71-IA~1\\LOCALA~1\\CRANLI~1"
p <- "//Rixdsntp001/cmcstat/7~1.STA/71-IA~1/LOCALA~1/CRANLI~1"
```

```{r, eval=FALSE}
repopath <- "//Rixdsntp001/cmcstat/7. STAT ANALYSES and IA/71- IA/LocalApps/CRANlike-SL"
makeRepo(repopath, name="SL")
# this works (except the end message "Refer to this repo with:  c(SL = "file:///\\Rixdsntp001/cmcstat/7. STAT ANALYSES and IA/71- IA/LocalApps/CRANlike-SL") or c(SL = "file:\\Rixdsntp001/cmcstat/7. STAT ANALYSES and IA/71- IA/LocalApps/CRANlike-SL")"):
# no, issue tools::write_PACKAGES because of winslash="/" in normalizePath of tools:::file_path_as_absolute
# pourtant setwd(normalizePath(p, "/")) fonctionne ! 
# TODO essaye avec le shortNamePath 
repopath <- "Y:/7. STAT ANALYSES and IA/71- IA/LocalApps/CRANlike-SL"
addPackage(repopath, "../SLutils_1.4.11.tar.gz", binary=TRUE, testbuild=FALSE, oldeRversion=-1, multiarch=FALSE)
# this:
writePACKAGESandArchive(repopath)
```


## Repo "path" given by network drive name:

```{r}
repo <- c(SL="file:////RIXDSNTP001/CMCSTAT/7. STAT ANALYSES and IA/71- IA/LocalApps/CRANlike-SL")
repo <- c(SL="file:////Rixdsntp001/cmcstat/7. STAT ANALYSES and IA/71- IA/LocalApps/CRANlike-SL")
repo <- c(SL="file:////Rixdsntp001/cmcstat/7~1.STA/71-IA~1/LOCALA~1/CRANLI~1")
```

## install with dependencies 

```{r, eval=FALSE}
repo <- c(SL = "file:///U:/Data/CRANlike-SL")
repo <- c(SL="file:////Rixdsntp001/cmcstat/7~1.STA/71-IA~1/LOCALA~1/CRANLI~1")
repos <- c(repo, getOption("repos"))
install.packages("totalerror", repos=repos, type="binary", dependencies=TRUE)

```


## `devtools:::package_find_repo`

This finds only the old versions.

```{r}
repo <- c(SL="file:///U:/Data/CRANlike-SL/")
devtools:::package_find_repo("SLutils", repo)
```

et ça marche avec `devtools::install_version`

____

```{r, eval=FALSE}
repo <- c(SL="file:////RIXDSNTP001/CMCSTAT/7. STAT ANALYSES and IA/71- IA/LocalApps/CRANlike-SL")
repo <- c(SL="file:///U:/Data/CRANlike-SL/")
contriburl <- contrib.url(repo, "source")
available <- available.packages(contriburl) 
# voir si install.packages("SLutils", repos=NULL, contriburl=contriburl)
#   marche pour le network repo
contriburl <- contrib.url(repo, "binary")
available <- available.packages(contriburl)
# je pense (je sais pas en fait) que même si je ne déplace pas les 
#   fichiers bin je dois créer l'archive ?..
#   NON car même sans l'archive il trouve !!! 
# regarde ce que  ça donne avec un repo CRAN, as-tu les plusieurs versions ?
```

## `miniCRAN` 

Les fonctions de miniCRAN ne marchent pas => faire les modifs pour qu'elles marchent ? 
